---
title: "Midterm Problem Set"
author:
- Carlos Guilherme Cabrine
- Gabriel Tabak
- Gustavo Henrique
date: "2025-14-05"
output:
  html_document:
    toc: yes
    df_print: paged
  pdf_document:
    toc: yes
    number_sections: no
    latex_engine: xelatex
header-includes:
- \usepackage{xcolor, fancyhdr, amsmath, amssymb, amsthm, framed, cancel, float}
- \pagestyle{fancy}
---

```{=tex}
\fancypagestyle{plain}{\pagestyle{fancy}}
\fancyhead[L]{Topics in Labor and Demographic Economics}
\fancyhead[R]{PROF. ANDREA FLORES}
\renewcommand{\footrulewidth}{0.4pt}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\pagebreak

# Question 1:

```{r warning=FALSE, include=FALSE}
# Load the necessary libraries
library("ggplot2")
library("readr")
library("dplyr")
library("patchwork")
library("readxl")
```

```{r warning=FALSE, include=FALSE}

# Ler os dados - SDE

SDE_10 <- read_csv("G:/Data/2010trim1_csv/SDEMT110.csv")
SDE_10$Year <- 2010

SDE_11 <- read_csv("G:/Data/2011trim1_csv/SDEMT111.csv")
SDE_11$Year <- 2011

SDE_12 <- read_csv("G:/Data/2012trim1_csv/SDEMT112.csv")
SDE_12$Year <- 2012

SDE_13 <- read_csv("G:/Data/2013trim1_csv/SDEMT113.csv")
SDE_13$Year <- 2013

SDE_14 <- read_csv("G:/Data/2014trim1_csv/SDEMT114.csv")
SDE_14$Year <- 2014

SDE_15 <- read_csv("G:/Data/2015trim1_csv/SDEMT115.csv")
SDE_15$Year <- 2015

SDE_16 <- read_csv("G:/Data/2016trim1_csv/SDEMT116.csv")
SDE_16$Year <- 2016

SDE_17 <- read_csv("G:/Data/2017trim1_csv/SDEMT117.csv")
SDE_17$Year <- 2017

SDE_18 <- read_csv("G:/Data/2018trim1_csv/SDEMT118.csv")
SDE_18$Year <- 2018

SDE_19 <- read_csv("G:/Data/2019trim1_csv/SDEMT119.csv")
SDE_19$Year <- 2019

SDE_20 <- read_csv("G:/Data/2020trim1_csv/ENOE_SDEMT120.csv")
SDE_20$Year <- 2020

SDE_Total <- rbind(SDE_10,SDE_11,SDE_12,SDE_13,
                   SDE_14,SDE_15,SDE_16,SDE_17,
                   SDE_18,SDE_19,SDE_20)

rm(SDE_10,SDE_11,SDE_12,SDE_13,
   SDE_14,SDE_15,SDE_16,SDE_17,
   SDE_18,SDE_19,SDE_20)

# Ler dados - COE2
COE2_10 <- read_csv("G:/Data/2010trim1_csv/COE2T110.csv")
COE2_10$Year <- 2010

COE2_11 <- read_csv("G:/Data/2011trim1_csv/COE2T111.csv")
COE2_11$Year <- 2011

COE2_12 <- read_csv("G:/Data/2012trim1_csv/COE2T112.csv")
COE2_12$Year <- 2012

COE2_13 <- read_csv("G:/Data/2013trim1_csv/COE2T113.csv")
COE2_13$Year <- 2013

COE2_14 <- read_csv("G:/Data/2014trim1_csv/COE2T114.csv")
COE2_14$Year <- 2014

COE2_15 <- read_csv("G:/Data/2015trim1_csv/COE2T115.csv")
COE2_15$Year <- 2015

COE2_16 <- read_csv("G:/Data/2016trim1_csv/COE2T116.csv")
COE2_16$Year <- 2016

COE2_17 <- read_csv("G:/Data/2017trim1_csv/COE2T117.csv")
COE2_17$Year <- 2017

COE2_18 <- read_csv("G:/Data/2018trim1_csv/COE2T118.csv")
COE2_18$Year <- 2018

COE2_19 <- read_csv("G:/Data/2019trim1_csv/COE2T119.csv")
COE2_19$Year <- 2019

COE2_20 <- read_csv("G:/Data/2020trim1_csv/ENOE_COE2T120.csv")
COE2_20$Year <- 2020

COE2_Total <- rbind(COE2_10,COE2_11,COE2_12,COE2_13,
                    COE2_14,COE2_15,COE2_16,COE2_17,
                    COE2_18,COE2_19,COE2_20)

rm(COE2_10,COE2_11,COE2_12,COE2_13,
   COE2_14,COE2_15,COE2_16,COE2_17,
   COE2_18,COE2_19,COE2_20)

```

```{r warning=FALSE, include=FALSE}

# Ler dados - CPI 
MEXCPI <- read_excel("G:/Data/MEXCPI.xlsx", 
                     sheet = "Annual")
MEXCPI$Year <-  as.numeric(format(MEXCPI$observation_date, "%Y"))
colnames(MEXCPI)[2] <- "CPI"
MEXCPI$observation_date <- NULL

```

## (a)

Using the ENOE data set (SDEMT first quarter for the period between 2010-2020), we explored the labor market trends for women aged 25–65 by computing yearly mean real wages\footnote{All monetary values are expressed in real terms, adjusted to 2015 Mexican CPI levels.}, mean hours worked (both unconditional and conditional), and mean employment rates.

Real wages fell in the first eight years, recovering after 2018, ultimately returning to near their initial levels by the end of the period. Female labor market participation stands at 48-49\% at the beginning of the period and rose to around 53\% by the end. The rising employment rate aligns with broader trends of increasing female participation in Mexico. Conditional hours worked (\textit{i.e.}, for employed women) followed an unstable path, ending at $\sim$38.4 hours per week in 2020, suggesting fluctuations in full-time work intensity. Unconditional hours worked (including non-employed women as zeros) displayed a steady increase, surpassing 20 hours per week by 2020. The volatility in conditional hours worked may indicate shifts between part-time and full-time work, while the growth in unconditional hours underscores the expanding role of women in the labor market. These trends highlight the dynamics of female labor supply, with more women working and, in later years, earning higher real wages on average. 

```{r warning=FALSE, include=FALSE}

# Get some household variables 
SDE_Summ <- SDE_Total %>% group_by(cd_a, ent, con, v_sel,
                                   n_hog, h_mud, Year) %>%
  summarise(age_hhead = eda[which(par_c == 101)],
            age_hspouse = first(eda[par_c %in% c(201,202)]),
            chld_less16 = as.integer(sum(par_c %in% c(301,302,303) &
                                           eda < 16) > 0))
   

# Join with the data
SDE_Total <- SDE_Total %>% left_join(SDE_Summ, 
                                     by = c("cd_a", "ent", "con",
                                            "v_sel", "n_hog", "h_mud",
                                            "Year")
                                     )


# Employed 
# hrsocu > 0 and non empty, also, age_hhead > 13 and age_hhead <= 98

SDE_Total <- SDE_Total %>% mutate(Employed = ifelse((hrsocup >0) & 
                                                      (age_hhead <= 98) &
                                                      (age_hhead > 13),
                                                    1, 0))

# Get the conditional hours
SDE_Total$HourC <- ifelse(SDE_Total$Employed == 1,
                          SDE_Total$hrsocup, NA)

#Deflate the salary
SDE_Total <- SDE_Total %>% left_join(MEXCPI, by = c("Year"))
#SDE_Total <- SDE_Total %>% mutate(Wage = 12*ingocup*(100/CPI))
SDE_Total <- SDE_Total %>% mutate(Wage = 52*ing_x_hrs*hrsocup*(100/CPI))  

#ggplot(SDE_Total, aes(Wage)) + geom_histogram()

df1 <- SDE_Total %>% 
  filter(sex == 2, 
         eda %in% 25:65) %>% 
  group_by(Year) %>%
  summarise(EmplR = mean(Employed),
            YWage = mean(Wage),
            Hrs = mean(hrsocup),
            HrsC = mean(HourC, na.rm = T))
  
df1$Year <- as.factor(df1$Year)

g1 <- ggplot(df1, aes(Year,EmplR)) + geom_point() + 
  geom_line(aes(group = 1)) + theme_bw() +
  ylab("Employment")
#ggsave("plot1.png",dpi=600)

g2 <- ggplot(df1, aes(Year,YWage)) + geom_point() + 
  geom_line(aes(group = 1)) +theme_bw() +
  ylab("Mean Yearly Wage")
#ggsave("plot2.png",dpi=600)

g3 <- ggplot(df1, aes(Year,Hrs)) + geom_point() + 
  geom_line(aes(group = 1)) + theme_bw() +
  ylab("Hours Occupied by week Unconditionl")
#ggsave("plot3.png",dpi=600)

g4 <- ggplot(df1, aes(Year,HrsC)) + geom_point() + 
  geom_line(aes(group = 1)) + theme_bw() +
  ylab("Hours Occupied by week Conditionl")
#ggsave("plot4.png",dpi=600)

print((g1 | g2) / (g3 | g4))
# ggsave("plot1.png",dpi=600)


```


## (b)

```{r}

df <- SDE_Total %>% filter(sex == 2,
                           eda %in% 25:65)


df$hj_peq <- ifelse(df$n_hij != 0 & df$chld_less16 != 0 &
                      (df$par_c %in% c(101,201)), 1, 0)


Tables <- function(df1, status){
  df1 <- df1 %>% filter(e_con == status)
  
  final <- matrix(0, 5, 8)
  final <- data.frame(final)
  
  # All
  final[1,c(1,5)] <- c(mean(df1$Employed), mean(df1$Wage/12))
  
  final[1,c(2,6)] <- df1 %>% filter(cs_p13_1 < 4) %>%
    summarise(mean(Employed), mean(Wage/12)) %>% as.numeric()
  
  final[1,c(3,7)] <- df1 %>% filter(cs_p13_1 == 4) %>% 
    summarise(mean(Employed), mean(Wage/12)) %>% as.numeric()
  
  final[1,c(4,8)] <- df1 %>% filter(cs_p13_1 %in% c(7,8,9)) %>% 
    summarise(mean(Employed), mean(Wage/12)) %>% as.numeric()
  
  
  # Less than 35 with young child
  final[2,c(1,5)] <- df1 %>% filter(hj_peq == 1, eda < 35) %>% 
    summarise(mean(Employed), mean(Wage/12)) %>% as.numeric()
  
  final[2,c(2,6)] <- df1 %>% filter(hj_peq == 1, eda < 35, cs_p13_1 < 4) %>% 
    summarise(mean(Employed), mean(Wage/12))%>% as.numeric()
  
  final[2,c(3,7)] <- df1 %>% filter(hj_peq == 1, eda < 35, cs_p13_1 == 4) %>% 
    summarise(mean(Employed), mean(Wage/12))%>% as.numeric()
  
  final[2,c(4,8)] <- df1 %>% filter(hj_peq == 1, eda < 35,cs_p13_1 %in% c(7,8,9)) %>%
    summarise(mean(Employed), mean(Wage/12))%>% as.numeric()
  
  
  # Less than 35 with no child
  final[3,c(1,5)] <- df1 %>% filter(hj_peq == 0, eda < 35) %>% 
    summarise(mean(Employed), mean(Wage/12))%>% as.numeric()
  
  final[3,c(2,6)] <- df1 %>% filter(hj_peq == 0, eda < 35,cs_p13_1 < 4) %>%
    summarise(mean(Employed), mean(Wage/12))%>% as.numeric()
  
  final[3,c(3,7)] <- df1 %>% filter(hj_peq == 0, eda < 35,cs_p13_1 == 4) %>%
    summarise(mean(Employed), mean(Wage/12))%>% as.numeric()
  
  final[3,c(4,8)] <- df1 %>% filter(hj_peq == 0, eda < 35,cs_p13_1 %in% c(7,8,9)) %>%
    summarise(mean(Employed), mean(Wage/12))%>% as.numeric()
  
  
  # Edad: 35-54
  final[4,c(1,5)] <- df1 %>% filter(eda >= 35, eda<=54) %>% summarise(mean(Employed), mean(Wage/12))%>% as.numeric()
  
  final[4,c(2,6)] <- df1 %>% filter(eda >= 35, eda<=54,cs_p13_1 < 4) %>% 
    summarise(mean(Employed), mean(Wage/12))%>% as.numeric()
  
  final[4,c(3,7)] <- df1 %>% filter(eda >= 35, eda<=54,cs_p13_1 == 4) %>%
    summarise(mean(Employed), mean(Wage/12))%>% as.numeric()
  
  final[4,c(4,8)] <- df1 %>% filter(eda >= 35, eda<=54,cs_p13_1 %in% c(7,8,9)) %>%
    summarise(mean(Employed), mean(Wage/12))%>% as.numeric()
  
  
  # Edad: 55+
  final[5,c(1,5)] <- df1 %>% filter(eda >= 55) %>% 
    summarise(mean(Employed), mean(Wage/12))%>% as.numeric()
  
  final[5,c(2,6)] <- df1 %>% filter(eda >= 55,cs_p13_1 < 4) %>% 
    summarise(mean(Employed), mean(Wage/12))%>% as.numeric()
  
  final[5,c(3,7)] <- df1 %>% filter(eda >= 55,cs_p13_1 == 4) %>%
    summarise(mean(Employed), mean(Wage/12))%>% as.numeric()
  
  final[5,c(4,8)] <- df1 %>% filter(eda >= 55,cs_p13_1 %in% c(7,8,9)) %>%
    summarise(mean(Employed), mean(Wage/12))%>% as.numeric()
  
  rownames(final) <- c("All", "Less 35 - Young Chld",
                       "Less 35 - No Chld", "35-54",
                       "55+")
  
  colnames(final) <- c("All", "Less HS", "HS", "College+",
                       "All - W", "Less HS - W", "HS - W", "College+ - W")  
  return(final)
}
# status = 5 (Married), 1 (Cohabiting), 6 (Single)
# rm(dfM); rm(dfC); rm(dfS); rm(status)

```

```{r}

dfM <- Tables(df,5)
print(dfM)

```

```{r}

dfC <- Tables(df,1)
print(dfC)

```

```{r}

dfS <- Tables(df,6)
print(dfS)

```
As expected, employment rate and earnings are lower for women with low educational levels. Single women exhibit the highest labor force participation, with employment rates around 70\% overall, peaking at 52\% for those under 55. In contrast, married women show significantly lower employment rates (42\% overall), particularly among older groups (close to 30\% for those 55+). Cohabiting women fall between these two groups, with employment rates around 46\% overall. The presence of children reduces employment probabilities, especially for partnered women under 35.  employment rate drops from 49\% (no small children) to 46\% (with children under 16).

Wage patterns mirror the employment trends. Single women earn substantially more (2703.54 pesos weekly on average) than their married (1623.60 pesos) and cohabiting (1655.12 pesos) counterparts. The wage gap persists across age groups, with prime-age (35-54) single women earning nearly double what married women of the same age earn. Children appear to negatively impact earnings, particularly for married women under 35, whose weekly wages are about 23\% lower if they have children. Older women (55+) experience a sharp decline in wages across all marital statuses (which might be due, in part, to retirement), though single women maintain a relative advantage. 

These patterns suggest that marriage and child-bearing remain significant barriers to women's labor market participation and earnings in Mexico. The substantial gaps between single and partnered women likely reflect both cultural norms around caregiving responsibilities and potential labor market discrimination against mothers. The particularly relative low employment and wages of older women indicate additional challenges in workforce retention later in life.


## (c)

```{r}

df2 <- COE2_Total %>% select("cd_a", "ent", "con",
                             "v_sel", "n_hog", "h_mud",
                             "n_ren", "n_pro_viv",
                             "Year", "p11_h2", "p11_m2", 
                             "p11_h7", "p11_m7" , "p11_h5", "p11_m5")


## household chores W
df <- SDE_Total %>% filter(e_con %in% c(1,5),
                           sex == 2,
                           eda %in% 25:65,
                           par_c %in% c(101,201))


# Remove pairs with 2 W
Aux <- df %>% group_by(cd_a, ent, con,
                       v_sel, n_hog, h_mud, Year) %>% 
  summarise(n = n()) %>% filter(n>1) 

X <- paste(df$cd_a, df$ent, df$con, df$v_sel,
           df$n_hog, df$h_mud, df$Year)
X2 <- paste(Aux$cd_a, Aux$ent, Aux$con, Aux$v_sel,
            Aux$n_hog, Aux$h_mud, Aux$Year)

df <- df[!X%in%X2,]

rm(X); rm(X2); rm(Aux)


# Join with the COE2
df <- left_join(df, df2 , by = c("cd_a", "ent", "con",
                                 "v_sel", "n_hog", "h_mud",
                                 "n_ren", "n_pro_viv",
                                 "Year"))


df$p11_h2 <- ifelse(is.na(df$p11_h2), 0, df$p11_h2)
df$p11_h5 <- ifelse(is.na(df$p11_h5), 0, df$p11_h5)
df$p11_h7 <- ifelse(is.na(df$p11_h7), 0, df$p11_h7)
df$p11_m2 <- ifelse(is.na(df$p11_m2), 0, df$p11_m2)
df$p11_m5 <- ifelse(is.na(df$p11_m5), 0, df$p11_m5)
df$p11_m7 <- ifelse(is.na(df$p11_m7), 0, df$p11_m7)


df <- df %>% filter(p11_h2 != 98, p11_h5 != 98, p11_h7 != 98)


df$p11_h2 <- ifelse(df$p11_h2 == 99 | is.na(df$p11_h2), 0, df$p11_h2)
df$p11_h5 <- ifelse(df$p11_h5 == 99 | is.na(df$p11_h5), 0, df$p11_h5)
df$p11_h7 <- ifelse(df$p11_h7 == 99 | is.na(df$p11_h7), 0, df$p11_h7)


df$hhChores_W <- ifelse(df$Year < 2013,  df$p11_h2*60 + df$p11_m2 +
                                         df$p11_h5*60 + df$p11_m5,0)
df$hhChores_W <- ifelse(df$Year >= 2013, df$p11_h2*60 + df$p11_m2 +
                                         df$p11_h7*60 + df$p11_m7, df$hhChores_W)


df %>% ggplot() + geom_histogram(mapping = aes(hhChores_W/60))



## household chores man

dfM <- SDE_Total %>% filter(e_con %in% c(1,5),
                            sex == 1,
                            par_c %in% c(101,201))


# Remove pairs with 2 M
Aux <- dfM %>% group_by(cd_a, ent, con,
                        v_sel, n_hog, h_mud, Year) %>% 
  summarise(n = n()) %>% filter(n>1) 

X <- paste(dfM$cd_a, dfM$ent, dfM$con, dfM$v_sel,
           dfM$n_hog, dfM$h_mud, dfM$Year)
X2 <- paste(Aux$cd_a, Aux$ent, Aux$con, Aux$v_sel,
            Aux$n_hog, Aux$h_mud, Aux$Year)

dfM <- dfM[!X%in%X2,]

rm(X); rm(X2); rm(Aux)


# Join with the COE2
dfM <- left_join(dfM, df2 , by = c("cd_a", "ent", "con",
                                   "v_sel", "n_hog", "h_mud",
                                   "n_ren", "n_pro_viv",
                                   "Year"))


dfM$p11_h2 <- ifelse(is.na(dfM$p11_h2), 0, dfM$p11_h2)
dfM$p11_h5 <- ifelse(is.na(dfM$p11_h5), 0, dfM$p11_h5)
dfM$p11_h7 <- ifelse(is.na(dfM$p11_h7), 0, dfM$p11_h7)
dfM$p11_m2 <- ifelse(is.na(dfM$p11_m2), 0, dfM$p11_m2)
dfM$p11_m5 <- ifelse(is.na(dfM$p11_m5), 0, dfM$p11_m5)
dfM$p11_m7 <- ifelse(is.na(dfM$p11_m7), 0, dfM$p11_m7)


dfM <- dfM %>% filter(p11_h2 != 98, p11_h5 != 98, p11_h7 != 98)


dfM$p11_h2 <- ifelse(dfM$p11_h2 == 99 | is.na(dfM$p11_h2), 0, dfM$p11_h2)
dfM$p11_h5 <- ifelse(dfM$p11_h5 == 99 | is.na(dfM$p11_h5), 0, dfM$p11_h5)
dfM$p11_h7 <- ifelse(dfM$p11_h7 == 99 | is.na(dfM$p11_h7), 0, dfM$p11_h7)


dfM$hhChores_M <- ifelse(dfM$Year < 2013,  dfM$p11_h2*60 + dfM$p11_m2 +
                           dfM$p11_h5*60 + dfM$p11_m5,0)
dfM$hhChores_M <- ifelse(dfM$Year >= 2013, dfM$p11_h2*60 + dfM$p11_m2 +
                           dfM$p11_h7*60 + dfM$p11_m7, dfM$hhChores_M)


dfM %>% ggplot() + geom_histogram(mapping = aes(hhChores_M/60))


dfM <- dfM %>% select(cd_a, ent, con, v_sel, n_hog, 
                      h_mud, n_ren, n_pro_viv, Year, hhChores_M)

#### Join- W + M

df <- df %>% left_join(dfM, by = c("cd_a", "ent", "con",
                                   "v_sel", "n_hog", "h_mud",
                                   "Year"))

df <- df[!is.na(df$hhChores_M),]

#ggplot(df, aes(hhChores_M, hhChores_M)) +geom_point()

df %>% filter(e_con == 1) %>%
  group_by(Year) %>% 
  summarise(Ratio = mean(hhChores_W/(hhChores_M + hhChores_W), na.rm = T))

df %>% filter(e_con == 5) %>%
  group_by(Year) %>% 
  summarise(Ratio = mean(hhChores_W/(hhChores_M + hhChores_W), na.rm = T))

df %>% 
  group_by(Year, e_con) %>% 
  summarise(Ratio = mean(hhChores_W/(hhChores_M + hhChores_W), na.rm = T)) %>%
  ggplot(mapping = aes(Year, Ratio, col = as.factor(e_con))) + geom_point() +
  geom_line() + theme_bw()


rm(df2); rm(dfM)

# SDE_Total %>% filter(cd_a == 1, ent == 9, con == 40023,
#                      v_sel == 2, n_hog == 1, h_mud == 0) %>%
#   select(cd_a, ent, con, v_sel, n_hog, h_mud,Year,sex,
#          eda,par_c, n_hij, chld_less16) %>%
#   View()


```

We calculated women's share of housework hours within heterosexual couples. Our sample included working-age women who were either household heads or spouses of heads, matched with their most likely male partners (either household heads or spouses) from the same household. We excluded same-sex couples.

The female share of housework ($R$) was computed using, 
$$R = \frac{H_w}{H_w + H_s}$$
in which $H_w$ represents woman's weekly housework hours and $H_s$ denotes her male spouse's weekly housework hours.

The ratio in Figure \ref{} provides a measure of the relative domestic burden on women within partnered households, either married or cohabiting. 


## (d)

```{r}

VivEni <- read_csv("G:/Data/viviendas.csv")
ConcEni <- read_csv("G:/Data/concentradohogar.csv")
PobEni <- read_csv("G:/Data/poblacion.csv")
GasEni <- read_csv("G:/Data/gastoshogar.csv")

# Get Home Ownership
VivEni <- VivEni %>% 
  filter(tenencia != 6) %>%
  mutate(homeownership = ifelse(tenencia %in% c(1,2,5), 0, 1))

# Get daycar, insurances, child care
GasEni <- GasEni %>% mutate(health_ins = ifelse(clave %in% c("J070", "J071", "J072"),
                                                gasto_tri, 0),
                            other_ins  = ifelse(clave %in% c("N008", "N009"),
                                               gasto_tri, 0),
                            child_care = ifelse(clave %in% c("E012"),
                                                gasto_tri, 0),
                            child_exp  = ifelse(!is.na(clave),
                                                as.integer(clave == "E012"), NA),
                            day_care = ifelse(clave %in% c("E008"),
                                                gasto_tri, 0),
                            day_exp  = ifelse(!is.na(clave),
                                                as.integer(clave == "E008"), NA)
                            )


GasH <- GasEni %>% group_by(folioviv, foliohog) %>%
  summarise(health_ins = sum(health_ins, na.rm = T),
            other_ins  = sum(other_ins, na.rm = T),
            child_care = sum(child_care, na.rm = T),
            child_exp  = sum(child_exp, na.rm = T),
            day_care   = sum(day_care, na.rm = T),
            day_exp    = sum(day_exp, na.rm = T))


PobH <- PobEni %>% group_by(folioviv, foliohog) %>%
  summarise(age_hhead = edad[which(parentesco == 101)],
            age_hspouse = first(edad[parentesco %in% c(201,202)]),
            married = edo_conyug[which(parentesco == 101)])




ConcEni <- ConcEni %>% left_join(VivEni, by = c("folioviv"))

ConcEni <- ConcEni %>% left_join(GasH, by = c("folioviv",
                                              "foliohog"))

ConcEni <- ConcEni %>% left_join(PobH, by = c("folioviv",
                                              "foliohog"))


ConcEni <- ConcEni %>% 
  filter(clase_hog == 2)


ConcEni <- ConcEni %>% mutate(Income = ing_cor - ingtrab,
                              Food =  ali_dentro + ali_fuera,
                              Transportation = transporte,
                              HealthService = salud,
                              Utilities = pred_cons + agua + energia,
                              Education = educacion,
                              HouseKeeping = cuidados,
                              Rent = ifelse(homeownership == 0, alquiler, estim_alqu),
                              Insurance = health_ins + other_ins,
                              Health_ins = health_ins,
                              Home_ins = other_ins,
                              Childc = day_care + child_care)



vars_to_summarise <- c("Income", "Food", "Transportation", "HealthService", "Utilities", 
                       "Education", "HouseKeeping", "Rent", "Insurance", "Health_ins", 
                       "Home_ins", "Childc")



tabela_resumo <- ConcEni %>%
  filter(married %in% c(1, 2)) %>%
  group_by(married) %>%
  summarise(
    across(all_of(vars_to_summarise),
           list(Mean = ~mean(.x, na.rm = TRUE),
                Median = ~median(.x, na.rm = TRUE)))
  )
```

```{r}

tabela_resumo

```
