---
title: 'Topics in Labor & Demo: Midterm Problem Set'
author: "Gabriel Tabak, Guilherme Cabrine & Gustavo Henrique"
date: '`r Sys.Date()`'
output: pdf_document
encoding: UTF-8
---


```{r, echo=FALSE}
## Loading/Installing needed packages
pacman::p_load(tidyverse,
               estimatr,
               stats,
               stargazer,
               haven,
               here,
               patchwork,
               readxl)
```

# Question 1

```{r, echo=FALSE}
## Importing databases
# Importing SDEM final dataset
sdem = read_csv(here("Data/Final", "sdem.csv"))

# Cleaning memory
gc()

# Price index Data
mexcpi = read_excel(here("Data/Raw", "MEXCPIALLAINMEI.xlsx"),
                     sheet = "Annual") %>% 
  mutate(year = as.numeric(format(observation_date, "%Y"))) %>% 
  rename(cpi = MEXCPIALLAINMEI) %>% 
  select(-1)
```

### Item a
```{r, echo=FALSE}
# Get some household variables 
sdem_agg = sdem %>% group_by(cd_a, ent, con, v_sel, n_hog, h_mud, year) %>%
  summarise(age_hhead = eda[which(par_c == 101)],
            age_hspouse = first(eda[par_c %in% c(201,202)]),
            chld_less16 = as.integer(sum(par_c %in% c(301,302,303) &
                                           eda < 16) > 0))

# Join with the data
sdem = sdem %>% 
  left_join(sdem_agg)

# Removing unneeded df
rm(sdem_agg)

## Employed 
# hrsocu > 0 and non empty, also, age_hhead > 13 and age_hhead <= 98
sdem = sdem %>%
  mutate(Employed = ifelse((hrsocup >0) & (age_hhead <= 98) & (age_hhead > 13),
                                                    1, 0))

# Get the conditional hours
sdem$HourC = ifelse(sdem$Employed == 1,
                    sdem$hrsocup, 
                    NA)

# Deflate the salary
sdem = sdem %>% 
  left_join(mexcpi, by = c("year"))

sdem = sdem %>%
  mutate(Wage = 52*ing_x_hrs*hrsocup*(100/cpi))  

df1 = sdem %>% 
  filter(sex == 2, 
         eda %in% 25:65) %>% 
  group_by(year) %>%
  summarise(EmplR = mean(Employed),
            YWage = mean(Wage),
            Hrs = mean(hrsocup),
            HrsC = mean(HourC, na.rm = T)) %>% 
  mutate(year = as.factor(year))

g1 = ggplot(df1, aes(year, EmplR)) + geom_point() + 
  geom_line(aes(group = 1)) + theme_bw() +
  ylab("Employment")

g2 = ggplot(df1, aes(year, YWage)) + geom_point() + 
  geom_line(aes(group = 1)) +theme_bw() +
  ylab("Mean yearly Wage")

g3 = ggplot(df1, aes(year, Hrs)) + geom_point() + 
  geom_line(aes(group = 1)) + theme_bw() +
  ylab("Hours Occupied by week Unconditionl")

g4 = ggplot(df1, aes(year, HrsC)) + geom_point() + 
  geom_line(aes(group = 1)) + theme_bw() +
  ylab("Hours Occupied by week Conditionl")

(g1 | g2) / (g3 | g4)
ggsave(here("Out", "plot1.png"), width = 12, height = 12, dpi=600)

rm(g1, g2, g3, g4, df1)
```

### Item b
```{r, echo=FALSE}
# DATA PREPARATION SECTION
# Filter the main dataset (sdem) to include only women aged 25-65 and create child indicator
df = sdem %>%
  filter(sex == 2, eda %in% 25:65) %>%  # Filter for females (sex == 2) aged 25-65
  mutate(hj_peq = case_when(
    # Create indicator for women with young children: 1 if has children AND has child under 16 AND is in partnership
    n_hij != 0 & chld_less16 != 0 & (par_c %in% c(101,201)) ~ 1,
    T ~ 0  # Otherwise assign 0 (no young children or not in partnership)
  ))

# MAIN TABLE GENERATION FUNCTION
# Function to create summary statistics tables by marital status
Tables = function(df1, status){
  # Filter dataset by specific marital status (5=married, 1=cohabiting, 6=single)
  df1 = df1 %>% 
    filter(e_con == status)
  
  # Initialize empty 5x8 matrix to store results (5 age groups, 8 columns for stats)
  final = matrix(0, 5, 8)
  final = data.frame(final)
  
  # ROW 1: ALL WOMEN (regardless of age/children status)
  # Columns 1&5: Overall employment rate and weekly earnings for all women
  final[1,c(1,5)] = c(mean(df1$Employed), mean(df1$Wage/52))
  
  # Columns 2&6: Employment rate and weekly earnings for women with less than high school education
  final[1,c(2,6)] = df1 %>% 
    filter(cs_p13_1 < 4) %>%  # Education level less than 4 (less than HS)
    summarise(mean(Employed), mean(Wage/52)) %>%
    as.numeric()
  
  # Columns 3&7: Employment rate and weekly earnings for women with high school education
  final[1,c(3,7)] = df1 %>% 
    filter(cs_p13_1 == 4) %>%  # Education level equals 4 (high school)
    summarise(mean(Employed), mean(Wage/52)) %>%
    as.numeric()
  
  # Columns 4&8: Employment rate and weekly earnings for women with college or above
  final[1,c(4,8)] = df1 %>%
    filter(cs_p13_1 %in% c(7,8,9)) %>%  # Education levels 7,8,9 (college or above)
    summarise(mean(Employed), mean(Wage/52)) %>%
    as.numeric()
  
  # ROW 2: WOMEN UNDER 35 WITH YOUNG CHILDREN
  # Overall stats for women under 35 with young children
  final[2,c(1,5)] = df1 %>% 
    filter(hj_peq == 1, eda < 35) %>%  # Has young child indicator = 1 AND age < 35
    summarise(mean(Employed), mean(Wage/52)) %>%
    as.numeric()
  
  # Same group broken down by education levels (less than HS)
  final[2,c(2,6)] = df1 %>% 
    filter(hj_peq == 1, eda < 35, cs_p13_1 < 4) %>% 
    summarise(mean(Employed), mean(Wage/52)) %>%
    as.numeric()
  
  # Same group broken down by education levels (high school)
  final[2,c(3,7)] = df1 %>% 
    filter(hj_peq == 1, eda < 35, cs_p13_1 == 4) %>% 
    summarise(mean(Employed), mean(Wage/52)) %>%
    as.numeric()
  
  # Same group broken down by education levels (college+)
  final[2,c(4,8)] = df1 %>% 
    filter(hj_peq == 1, eda < 35,cs_p13_1 %in% c(7,8,9)) %>%
    summarise(mean(Employed), mean(Wage/52)) %>%
    as.numeric()
  
  # ROW 3: WOMEN UNDER 35 WITH NO SMALL CHILDREN
  # Overall stats for women under 35 without young children
  final[3,c(1,5)] = df1 %>% 
    filter(hj_peq == 0, eda < 35) %>%  # No young child indicator = 0 AND age < 35
    summarise(mean(Employed), mean(Wage/52)) %>%
    as.numeric()
  
  # Same group broken down by education levels (less than HS, HS, college+)
  final[3,c(2,6)] = df1 %>%
    filter(hj_peq == 0, eda < 35,cs_p13_1 < 4) %>%
    summarise(mean(Employed), mean(Wage/52)) %>%
    as.numeric()
  
  final[3,c(3,7)] = df1 %>%
    filter(hj_peq == 0, eda < 35,cs_p13_1 == 4) %>%
    summarise(mean(Employed), mean(Wage/52)) %>%
    as.numeric()
  
  final[3,c(4,8)] = df1 %>% 
    filter(hj_peq == 0, eda < 35,cs_p13_1 %in% c(7,8,9)) %>%
    summarise(mean(Employed), mean(Wage/52)) %>%
    as.numeric()
  
  # ROW 4: WOMEN AGED 35-54
  # Overall stats for middle-aged women (35-54)
  final[4,c(1,5)] = df1 %>% 
    filter(eda >= 35, eda<=54) %>%  # Age between 35 and 54
    summarise(mean(Employed), mean(Wage/52)) %>%
    as.numeric()
  
  # Same group broken down by education levels
  final[4,c(2,6)] = df1 %>%
    filter(eda >= 35, eda<=54,cs_p13_1 < 4) %>% 
    summarise(mean(Employed), mean(Wage/52)) %>%
    as.numeric()
  
  final[4,c(3,7)] = df1 %>%
    filter(eda >= 35, eda<=54,cs_p13_1 == 4) %>%
    summarise(mean(Employed), mean(Wage/52)) %>%
    as.numeric()
  
  final[4,c(4,8)] = df1 %>%
    filter(eda >= 35, eda<=54,cs_p13_1 %in% c(7,8,9)) %>%
    summarise(mean(Employed), mean(Wage/52)) %>%
    as.numeric()
  
  # ROW 5: WOMEN AGED 55 AND OLDER
  # Overall stats for older women (55+)
  final[5,c(1,5)] = df1 %>% 
    filter(eda >= 55) %>%  # Age 55 and above
    summarise(mean(Employed), mean(Wage/52)) %>%
    as.numeric()
  
  # Same group broken down by education levels
  final[5,c(2,6)] = df1 %>% 
    filter(eda >= 55,cs_p13_1 < 4) %>% 
    summarise(mean(Employed), mean(Wage/52)) %>%
    as.numeric()
  
  final[5,c(3,7)] = df1 %>% 
    filter(eda >= 55,cs_p13_1 == 4) %>%
    summarise(mean(Employed), mean(Wage/52)) %>%
    as.numeric()
  
  final[5,c(4,8)] = df1 %>% 
    filter(eda >= 55,cs_p13_1 %in% c(7,8,9)) %>%
    summarise(mean(Employed), mean(Wage/52)) %>%
    as.numeric()
  
  # Assign descriptive row names for the 5 age/family status groups
  rownames(final) = c("All", "Less than 35 with Child Younger than 16",
                      "Less than 35 with No Small Children", "35-54",
                      "55 and Older")
  
  # Assign column names: first 4 columns for labor force participation, last 4 for earnings
  colnames(final) = c("All", "Less than HS", "High School", "College or Above",
                      "All", "Less than HS", "High School", "College or Above")  
  return(final)
}

# LATEX TABLE GENERATION FUNCTION
# Function to convert data tables into professionally formatted LaTeX tables
create_final_table = function(df, status, status_name, output_file = NULL) {
  # Generate the data table using the Tables function
  table_data = Tables(df, status)
  
  # Create a clean label name for LaTeX referencing (lowercase, hyphens instead of spaces)
  label_name = tolower(gsub(" ", "-", status_name))
  
  # Build LaTeX table code following professional academic formatting standards
  latex_code = c(
    "\\begin{table}[htbp]",  # Table environment with positioning options
    "    \\centering",        # Center the table
    paste("    \\caption{Labor Force Participation and Earnings -", status_name, "Aged 25-65}"),  # Table caption
    paste("    \\label{tab:", label_name, "}", sep = ""),  # Table label for cross-referencing
    "    \\resizebox{\\textwidth}{!}{%",  # Resize table to fit page width
    "    \\begin{tabular}{lcccccccc}",    # Table structure: 1 left-aligned, 8 center-aligned columns
    "    \\toprule",  # Top horizontal line (booktabs package)
    # Create grouped column headers spanning multiple columns
    "     & \\multicolumn{4}{c}{\\textbf{Labor Force Participation}} & \\multicolumn{4}{c}{\\textbf{Earnings}} \\\\",
    "    \\cmidrule(lr){2-5} \\cmidrule(lr){6-9}",  # Partial horizontal lines under group headers
    # Individual column headers
    "     & All & Less than HS & High School & College+ & All & Less than HS & High School & College+ \\\\",
    "    \\midrule"  # Middle horizontal line separating headers from data
  )
  
  # Define row labels matching the data structure
  row_names = c("All", 
                "Less than 35 with Child Younger than 16",
                "Less than 35 with No Small Children", 
                "35-54",
                "55 and Older")
  
  # Add data rows to LaTeX code
  for(i in 1:nrow(table_data)) {
    # Format numbers to 3 decimal places for consistent presentation
    formatted_numbers = sprintf("%.3f", table_data[i,])
    # Construct each data row with proper LaTeX formatting
    data_row = paste("    ", row_names[i], " & ", 
                     paste(formatted_numbers, collapse = " & "),
                     " \\\\", sep = "")
    latex_code = c(latex_code, data_row)
  }
  
  # Close the LaTeX table structure
  latex_code = c(latex_code,
                 "    \\bottomrule",      # Bottom horizontal line
                 "    \\end{tabular}%",  # End tabular environment
                 "    }",                # Close resizebox
                 "    \\end{table}")     # End table environment
  
  # Output handling: save to file if specified, always print to console
  if(!is.null(output_file)) {
    writeLines(latex_code, output_file)  # Write LaTeX code to .tex file
  }
  
  cat(latex_code, sep = "\n")  # Display LaTeX code in console
  return(latex_code)           # Return code for further processing if needed
}

# BATCH TABLE GENERATION FUNCTION
# Utility function to generate all three required tables at once
generate_all_tables = function(df) {
  # Define the three marital status categories as specified in the problem set
  status_list = list(
    list(code = 5, name = "Married Women"),      # Marital status code 5
    list(code = 1, name = "Cohabiting Women"),   # Marital status code 1
    list(code = 6, name = "Single Women")        # Marital status code 6
  )
  
  # Loop through each marital status and generate corresponding table
  for(status_info in status_list) {
    # Print progress indicators for user feedback
    cat("\n", rep("=", 60), "\n")
    cat("GENERATING TABLE FOR:", status_info$name, "\n")
    cat(rep("=", 60), "\n")
    
    # Create standardized filename based on group name
    filename = paste0(tolower(gsub(" ", "_", status_info$name)), "_table.tex")
    # Generate the table
    create_final_table(df, status_info$code, status_info$name, filename)
    
    cat("\nTable saved to:", filename, "\n")
  }
}

# EXECUTION SECTION
# Generate all tables using the batch function
generate_all_tables(df)

# Alternative: Generate tables individually with specific file paths (using 'here' package for path management)
create_final_table(df, 5, "Married Women", here("Out", "married_women_final.tex"))
create_final_table(df, 1, "Cohabiting Women", here("Out", "cohabiting_women_final.tex")) 
create_final_table(df, 6, "Single Women", here("Out", "single_women_final.tex"))
```

### Item c
```{r, echo=FALSE}
## Household chores for Women
df = sdem %>% 
  filter(e_con %in% c(1,5),        # Marital status: cohabiting or married
         sex == 2,                 # Female
         eda %in% 25:65,           # Age filter as in Code 1
         par_c %in% c(101,201))    # Household head or spouse

## Household chores for Men
dfM = sdem %>% 
  filter(sex == 1,                 # Male - no marital status filter as in Code 1
         par_c %in% c(101,201))    # Household head or spouse - no age filter as in Code 1

# Remove unneeded dataframe
rm(sdem)

# Clean memory
gc()

# Remove households with 2 women (duplicates)
Aux = df %>% 
  group_by(cd_a, ent, con, v_sel, n_hog, h_mud, year) %>% 
  summarise(n = n()) %>% 
  filter(n > 1) 

X = paste(df$cd_a, df$ent, df$con, df$v_sel,
           df$n_hog, df$h_mud, df$year)
X2 = paste(Aux$cd_a, Aux$ent, Aux$con, Aux$v_sel,
            Aux$n_hog, Aux$h_mud, Aux$year)

df = df[!X %in% X2,]
rm(X, X2, Aux)

# Join with COE2 data if necessary (as in Code 1)
if(exists("df2")) {
  df = df %>% 
    left_join(df2, by = c("cd_a", "ent", "con", "v_sel", "n_hog", "h_mud",
                          "n_ren", "n_pro_viv", "year"))
}

# Handle missing values (NA treatment)
df$p11_h2 = ifelse(is.na(df$p11_h2), 0, df$p11_h2)
df$p11_h5 = ifelse(is.na(df$p11_h5), 0, df$p11_h5)
df$p11_h7 = ifelse(is.na(df$p11_h7), 0, df$p11_h7)
df$p11_m2 = ifelse(is.na(df$p11_m2), 0, df$p11_m2)
df$p11_m5 = ifelse(is.na(df$p11_m5), 0, df$p11_m5)
df$p11_m7 = ifelse(is.na(df$p11_m7), 0, df$p11_m7)

# Filter out "don't know" responses (code 98)
df = df %>% 
  filter(p11_h2 != 98, p11_h5 != 98, p11_h7 != 98)

# Handle "no response" codes (99) - convert to 0
df$p11_h2 = ifelse(df$p11_h2 == 99 | is.na(df$p11_h2), 0, df$p11_h2)
df$p11_h5 = ifelse(df$p11_h5 == 99 | is.na(df$p11_h5), 0, df$p11_h5)
df$p11_h7 = ifelse(df$p11_h7 == 99 | is.na(df$p11_h7), 0, df$p11_h7)

# Calculate household chores time for women (in minutes)
# Different variables used before and after 2013
df$hhChores_W = ifelse(df$year < 2013, df$p11_h2*60 + df$p11_m2 +
                                       df$p11_h5*60 + df$p11_m5, 0)
df$hhChores_W = ifelse(df$year >= 2013, df$p11_h2*60 + df$p11_m2 +
                                        df$p11_h7*60 + df$p11_m7, df$hhChores_W)

# Create histogram for women's household chores (in hours)
df %>% 
  ggplot() +
  geom_histogram(mapping = aes(hhChores_W/60)) +
  labs(title = "Distribution of Women's Household Chores (Hours)")

# Remove households with 2 men (duplicates)
Aux = dfM %>% 
  group_by(cd_a, ent, con, v_sel, n_hog, h_mud, year) %>% 
  summarise(n = n()) %>% 
  filter(n > 1) 

X = paste(dfM$cd_a, dfM$ent, dfM$con, dfM$v_sel,
           dfM$n_hog, dfM$h_mud, dfM$year)
X2 = paste(Aux$cd_a, Aux$ent, Aux$con, Aux$v_sel,
            Aux$n_hog, Aux$h_mud, Aux$year)

dfM = dfM[!X %in% X2,]
rm(X, X2, Aux)

# Join with COE2 data for men if necessary
if(exists("df2")) {
  dfM = dfM %>% 
    left_join(df2, by = c("cd_a", "ent", "con", "v_sel", "n_hog", "h_mud",
                          "n_ren", "n_pro_viv", "year"))
}

# Handle missing values for men
dfM$p11_h2 = ifelse(is.na(dfM$p11_h2), 0, dfM$p11_h2)
dfM$p11_h5 = ifelse(is.na(dfM$p11_h5), 0, dfM$p11_h5)
dfM$p11_h7 = ifelse(is.na(dfM$p11_h7), 0, dfM$p11_h7)
dfM$p11_m2 = ifelse(is.na(dfM$p11_m2), 0, dfM$p11_m2)
dfM$p11_m5 = ifelse(is.na(dfM$p11_m5), 0, dfM$p11_m5)
dfM$p11_m7 = ifelse(is.na(dfM$p11_m7), 0, dfM$p11_m7)

# Filter out "don't know" responses for men
dfM = dfM %>%
  filter(p11_h2 != 98, p11_h5 != 98, p11_h7 != 98)

# Handle "no response" codes for men
dfM$p11_h2 = ifelse(dfM$p11_h2 == 99 | is.na(dfM$p11_h2), 0, dfM$p11_h2)
dfM$p11_h5 = ifelse(dfM$p11_h5 == 99 | is.na(dfM$p11_h5), 0, dfM$p11_h5)
dfM$p11_h7 = ifelse(dfM$p11_h7 == 99 | is.na(dfM$p11_h7), 0, dfM$p11_h7)

# Calculate household chores time for men (in minutes)
dfM$hhChores_M = ifelse(dfM$year < 2013, dfM$p11_h2*60 + dfM$p11_m2 +
                                         dfM$p11_h5*60 + dfM$p11_m5, 0)
dfM$hhChores_M = ifelse(dfM$year >= 2013, dfM$p11_h2*60 + dfM$p11_m2 +
                                          dfM$p11_h7*60 + dfM$p11_m7, dfM$hhChores_M)

# Create histogram for men's household chores (in hours)
dfM %>%
  ggplot() + 
  geom_histogram(mapping = aes(hhChores_M/60)) +
  labs(title = "Distribution of Men's Household Chores (Hours)")

# Select necessary variables including wage and income variables
dfM = dfM %>%
  select(cd_a, ent, con, v_sel, n_hog, h_mud, year, hhChores_M,
         Wage, IngOcupYear)

# Rename male wage columns to distinguish from female wages
colnames(dfM)[9:10] = c("WageM", "IngOcupYearM")

#### Join Women + Men datasets
df = df %>%
  left_join(dfM, by = c("cd_a", "ent", "con", "v_sel", "n_hog", "h_mud", "year"))

# Remove observations without male household chores data
df = df[!is.na(df$hhChores_M),]

# Analysis by marital status - Cohabiting couples
df %>% filter(e_con == 1) %>%
  group_by(year) %>% 
  summarise(Ratio = mean(hhChores_W/(hhChores_M + hhChores_W), na.rm = T))

# Analysis by marital status - Married couples
df %>% filter(e_con == 5) %>%
  group_by(year) %>% 
  summarise(Ratio = mean(hhChores_W/(hhChores_M + hhChores_W), na.rm = T))

# Create enhanced plot showing household chores ratio by marital status
df %>% 
  group_by(year, e_con) %>% 
  summarise(Ratio = mean(hhChores_W/(hhChores_M + hhChores_W), na.rm = TRUE),
            childCare = mean(p11_h2, na.rm = TRUE)) %>%
  mutate(status = case_when(
    e_con == 1 ~ "Cohabiting",
    T ~ "Married"
  )) %>% 
  ggplot(aes(x = year, y = Ratio, color = as.factor(status))) + 
  geom_point() +
  geom_line() + 
  theme_bw() +
  labs(title = "Women's Share of Household Chores Over Time",
       y = "Women's Share of Total Household Chores",
       x = "Year",
       color = "Marital Status") + 
  scale_x_continuous(breaks = unique(df$year))

# Additional plot for child care hours (as in Code 1)
df %>% 
  group_by(year, e_con) %>% 
  summarise(childCare = mean(p11_h2, na.rm = T)) %>%
  mutate(status = case_when(
    e_con == 1 ~ "Cohabiting",
    T ~ "Married"
  )) %>% 
  ggplot(aes(x = year, y = childCare, color = as.factor(status))) + 
  geom_point() +
  geom_line() + 
  theme_bw() +
  labs(title = "Child Care Hours Over Time",
       y = "Child Care Hours", 
       x = "Year",
       color = "Marital Status") +
  scale_x_continuous(breaks = unique(df$year))

# Additional data cleaning - setup for advanced analysis (from Code 1)
df$constant = 1
dfMW = df %>% filter(e_con == 5)  # Married women
dfCW = df %>% filter(e_con == 1)  # Cohabiting women

# Calculate hourly wage and non-labor income
dfCW = dfCW %>% 
  mutate(HrlWage = ifelse(Employed == 1, Wage/(hrsocup*52), 0),
         nonLaborInc = ifelse(Wage + WageM == 0,
                              (IngOcupYear + IngOcupYearM)/52,
                              WageM/52))

dfMW = dfMW %>% 
  mutate(HrlWage = ifelse(Employed == 1, Wage/(hrsocup*52), 0),
         nonLaborInc = ifelse(Wage + WageM == 0,
                              (IngOcupYear + IngOcupYearM)/52,
                              WageM/52))

# Trim the top 1% richest (outlier removal)
dfMW = dfMW %>% 
  filter(nonLaborInc < quantile(nonLaborInc, 0.99, na.rm = TRUE),
         HrlWage < quantile(HrlWage, 0.99, na.rm = TRUE))

dfCW = dfCW %>% 
  filter(nonLaborInc < quantile(nonLaborInc, 0.99, na.rm = TRUE),
         HrlWage < quantile(HrlWage, 0.99, na.rm = TRUE))

# Additional cleaning filters
dfCW = dfCW %>% 
  filter(cs_p13_1 != 99,                    # Remove unknown education
         n_hij != 99,                       # Remove unknown number of children
         !((Employed == 1) & (Wage == 0)))  # Remove employed with zero wage

dfMW = dfMW %>% 
  filter(cs_p13_1 != 99,                    # Remove unknown education
         n_hij != 99,                       # Remove unknown number of children
         !((Employed == 1) & (Wage == 0)))  # Remove employed with zero wage

# Final cleanup
rm(df2, dfM, dfCW, dfMW)
gc()
```

### Item d
```{r, echo=FALSE}
## Importing databases
VivEni = read_csv(here("Data/Raw", "viviendas.csv"))
ConcEni = read_csv(here("Data/Raw", "concentradohogar.csv"))
PobEni = read_csv(here("Data/Raw", "poblacion.csv"))
GasEni = read_csv(here("Data/Raw", "gastoshogar.csv"))

# Get Home Ownership
VivEni = VivEni %>% 
  filter(tenencia != 6) %>%
  mutate(homeownership = ifelse(tenencia %in% c(1,2,5), 0, 1)) %>%
  select(folioviv, homeownership)  # Select only necessary columns as in Code 1

# Get daycare, insurances, child care
GasEni = GasEni %>% 
  mutate(health_ins = ifelse(clave %in% c("J070", "J071", "J072"),
                             gasto_tri, 0),
         other_ins  = ifelse(clave %in% c("N008", "N009"),
                            gasto_tri, 0),
         child_care = ifelse(clave %in% c("E012"),
                            gasto_tri, 0),
         child_exp  = ifelse(!is.na(clave),
                            as.integer(clave == "E012"), NA),
         day_care = ifelse(clave %in% c("E008"),
                          gasto_tri, 0),
         day_exp  = ifelse(!is.na(clave),
                          as.integer(clave == "E008"), NA))

# Aggregate household expenses by household
GasH = GasEni %>% 
  group_by(folioviv, foliohog) %>%
  summarise(health_ins = sum(health_ins, na.rm = T),
            other_ins  = sum(other_ins, na.rm = T),
            child_care = sum(child_care, na.rm = T),
            child_exp  = sum(child_exp, na.rm = T),
            day_care   = sum(day_care, na.rm = T),
            day_exp    = sum(day_exp, na.rm = T))

# Handle missing values in worked hours (assuming NA means not working)
PobEni = PobEni %>% 
  mutate(hor_1 = ifelse(is.na(hor_1), 0, hor_1),
         min_1 = ifelse(is.na(min_1), 0, min_1))

# Create household-level demographic and work variables
PobH = PobEni %>% 
  group_by(folioviv, foliohog) %>%
  summarise(age_hhead = edad[which(parentesco == 101)],
            age_hspouse = first(edad[parentesco %in% c(201,202)]),
            married = edo_conyug[which(parentesco == 101)],
            # Additional demographic variables from Code 1
            sex_hhead = sexo[which(parentesco == 101)],
            sex_hspouse = sexo[which(parentesco %in% c(201,202))],
            # Work hours variables (convert to minutes)
            hworked_hhead = 
              hor_1[which(parentesco == 101)]*60 + min_1[which(parentesco == 101)],
            hworked_hspouse = 
              hor_1[which(parentesco %in% c(201,202))]*60 + min_1[which(parentesco %in% c(201,202))],
            # Education variables
            sch_hhead = nivelaprob[which(parentesco == 101)],
            sch_hspouse = nivelaprob[which(parentesco %in% c(201,202))])

# Join all datasets
ConcEni = ConcEni %>% 
  left_join(VivEni, by = c("folioviv"))

ConcEni = ConcEni %>% 
  left_join(GasH, by = c("folioviv", "foliohog"))

ConcEni = ConcEni %>% 
  left_join(PobH, by = c("folioviv", "foliohog"))

# Filter for nuclear households only
ConcEni = ConcEni %>% 
  filter(clase_hog == 2)

# Create expense and income variables
ConcEni = ConcEni %>% 
  mutate(
    # Non-labor income (quarterly to monthly conversion)
    nonlabor_inc = (ing_cor - ingtrab)/3,
    # Expense categories
    food =  ali_dentro + ali_fuera,
    transportation = transporte,
    healthService = salud,
    utilities = pred_cons + agua + energia,
    education = educacion,
    houseKeeping = cuidados,
    # Rent calculation (actual rent or imputed rent)
    rent = ifelse(homeownership == 0, alquiler, estim_alqu),
    # Insurance categories
    insurance = health_ins + other_ins,
    health_ins = health_ins,
    home_ins = other_ins,
    # Child care expenses
    childc = day_care + child_care
  ) %>%
  # Select all necessary variables (expanded from Code 1)
  select(folioviv, foliohog, age_hhead, age_hspouse, married,
         homeownership, sex_hhead, sex_hspouse, hworked_hhead,
         hworked_hspouse, sch_hhead, sch_hspouse,
         nonlabor_inc, ingtrab, food, transportation,
         healthService, utilities, education, houseKeeping,
         rent, insurance, health_ins, home_ins, childc)

# Data cleaning steps from Code 1
# Remove observations with missing homeownership
ConcEni = ConcEni %>% 
  filter(!is.na(homeownership))

# Remove top 1% richest households (outlier removal)
ConcEni = ConcEni %>% 
  filter(nonlabor_inc < quantile(nonlabor_inc, 0.99, na.rm = TRUE),
         ingtrab < quantile(ingtrab, 0.99, na.rm = TRUE))

# Create additional processed variables
ConcEni = ConcEni %>%
  mutate(
    # Total consumption (quarterly to monthly conversion)
    total_consumption = (food + transportation +
      healthService + houseKeeping + health_ins +
      home_ins + utilities + childc + education + rent) / 3,
    # Convert work hours from minutes to hours
    hworked_hhead = hworked_hhead/60,
    hworked_hspouse = hworked_hspouse/60
  )

# Create separate datasets by marital status
dfMM = ConcEni %>% filter(married == 2)  # Married couples
dfCM = ConcEni %>% filter(married == 1)  # Cohabiting couples

# Define variables for summary statistics
vars_to_summarise = c("nonlabor_inc", "food", "transportation", "healthService", 
                      "utilities", "education", "houseKeeping", "rent", 
                      "insurance", "health_ins", "home_ins", "childc")

# Create comprehensive summary table
tabela_resumo = ConcEni %>%
  filter(married %in% c(1, 2)) %>%
  group_by(married) %>%
  summarise(
    across(all_of(vars_to_summarise),
           list(Mean = ~mean(.x, na.rm = TRUE),
                Median = ~median(.x, na.rm = TRUE)))
  )

# Display summary table
print(tabela_resumo)

# Optional: Check for missing values in key variables
# for (i in 1:ncol(dfMM)) {
#   cat("Variable:", colnames(dfMM)[i], "- Missing values:", sum(is.na(dfMM[,i])), "\n")
# }

# Clean up environment
rm(VivEni, GasEni, GasH, PobEni, PobH)
gc()
```

# Question 2


# Question 3


# Question 4
## Item a
### Interior solution
Considering positive work in both period 1 and 2, our Lagrangian is

$$\mathcal{L}=\sum_{t=1}^{3}\beta^{t-1}[\alpha \ln C_t+(1-\alpha)\ln L_t]-\lambda \left [\sum_{t=1}^{3} \frac{C_t}{(1+r)^{t-1}}-A_1-\sum_{t=1}^{2}\frac{w_t(L_0-L_t)}{(1+r)^{t-1}}\right]$$

with CPO's:

$$
\begin{aligned}
\,
[C_t] &: \frac{\alpha\beta^{t-1}}{C_t}-\frac{\lambda}{(1+r)^{t-1}}=0 \Longrightarrow C_t^*=\frac{\alpha[\beta(1+r)]^{t-1}}{\lambda} \\
[L_t] &: \frac{(1-\alpha)\beta^{t-1}}{L_t}-\frac{\lambda w_t}{(1+r)^{t-1}}=0 \Longrightarrow L_t^*=\frac{(1-\alpha)[\beta(1+r)]^{t-1}}{\lambda w_t}
\end{aligned}
$$

Then, the Frischian labor supply function is simple

$$
h_t^F(w_t, \lambda, t)=L_0-L_t^*=L_0-\frac{(1-\alpha)[\beta(1+r)]^{t-1}}{\lambda w_t}
$$

Recall that the Marshallian elasticity accounts for variations in labor supply due to permanent shocks in the path of wage. So, to find the Marshallian labor supply function, we need to substitute $C_t^*$ and $L_t^*$ into the budget constraint and isolate $\lambda$ to find a close expression for the Lagrangean multiplier, i. e.,

$$
\begin{aligned}
\sum_{t=1}^{3} \frac{C_t^*}{(1+r)^{t-1}}-A_1-\sum_{t=1}^{2}\frac{w_t(L_0-L_t^*)}{(1+r)^{t-1}} &= 0 \\
\sum_{t=1}^{3} \frac{1}{(1+r)^{t-1}} \cdot \frac{\alpha[\beta(1+r)]^{t-1}}{\lambda}-A_1-\sum_{t=1}^{2}\left[\frac{w_tL_0}{(1+r)^{t-1}}-\frac{w_t}{(1+r)^{t-1}}\cdot \frac{(1-\alpha)[\beta(1+r)]^{t-1}}{\lambda w_t}\right] &= 0 \\
\sum_{t=1}^{3} \frac{\alpha \beta^{t-1}}{\lambda}-A_1-\sum_{t=1}^{2}\left[\frac{w_tL_0}{(1+r)^{t-1}}-\frac{(1-\alpha)\beta^{t-1}}{\lambda}\right] &= 0 \\
\frac{\alpha}{\lambda}\sum_{t=1}^{3}\beta^{t-1}-A_1-L_0\sum_{t=1}^{2}\frac{w_t}{(1+r)^{t-1}}+\frac{(1-\alpha)}{\lambda}\sum_{t=1}^{2}\beta^{t-1} &= 0
\end{aligned}
$$

As we know

$$
\sum_{t=1}^{T}\beta^{t-1}=\frac{1-\beta^T}{1-\beta}
$$
So, we have

$$
\begin{aligned}
A_1+L_0\sum_{t=1}^{2}\frac{w_t}{(1+r)^{t-1}} &= \frac{1}{\lambda(1-\beta)}[\alpha(1-\beta^3)+(1-\alpha)(1-\beta^2)] \\
\lambda \left[A_1+L_0 \left(w_1+\frac{w_2}{(1+r)}\right)\right] &= \frac{1-\alpha \beta^3+(1-\alpha)\beta^2}{(1-\beta)} \\
\lambda \left [\frac{(1+r)(A_1+L_0 w_1)+w_2}{(1+r)} \right] &= \frac{1-\alpha \beta^3+(1-\alpha)\beta^2}{(1-\beta)} \\
\lambda^* &= \frac{(1+r)[1-\alpha \beta^3+(1-\alpha)\beta^2]}{(1-\beta)[(1+r)(A_1+L_0 w_1)+w_2]}
\end{aligned}
$$
Therefore, the Marshallian labor supply function is:

$$
\begin{aligned}
h_t^M(w_t, \lambda^*, t) &= L_0-\frac{(1-\alpha)[\beta(1+r)]^{t-1}}{\lambda^* w_t} \\
h_t^M(w_t, \lambda^*, t) &= L_0-\frac{\gamma(1-\alpha)[\beta(1+r)]^{t-1}}{w_t}
\end{aligned}
$$

where
$$
\gamma = \frac{(1-\beta)[(1+r)(A_1+L_0 w_1)+w_2]}{(1+r)[1-\alpha \beta^3+(1-\alpha)\beta^2]}
$$

### Corner solution
We have two cases to consider here:

1. **Work only in period 1 ($L_2=L_0$)**

In this case, the budget constraint will be

$$
\sum_{t=1}^{3} \frac{C_t}{(1+r)^{t-1}}=A_1+w_1(L_0-L_1)
$$
Notice that in this case we just need to choose $C_t$ and $L_1$, so the Lagrangean will be

$$
\mathcal{L}=\sum_{t=1}^{3}\beta^{t-1}\alpha \ln C_t+(1-\alpha)\ln L_1 + (\beta+\beta^2)(1-\alpha)L_0 + \lambda\left [A_1 + w_1(L_0-L_1)-\sum_{t=1}^3\frac{C_t}{(1+r)^{t-1}} \right]
$$

Then, from FOC we get and repeating the previous process, we get

$$
\begin{aligned}
h_1^F(w_1, \lambda)&=L_0-\frac{1-\alpha}{\lambda w_1} \\
h_1^M(w_1, \lambda^*, t)&=L_0-\frac{\gamma'(1-\alpha)}{w_1}
\end{aligned}
$$

where here

$$
\gamma'=\frac{(1-\beta)[A_1+w_1L_0]}{1-[1-\alpha(1-\beta^2)]\beta}
$$

2. **Work only in period 2 ($L_1=L_0$)**

The budget constraint in this case is

$$
\sum_{t=1}^{3} \frac{C_t}{(1+r)^{t-1}}=A_1+\frac{w_2(L_0-L_2)}{(1+r)}
$$
The Lagrangean then will be

$$
\mathcal{L}=\sum_{t=1}^{3}\beta^{t-1}\alpha \ln C_t+\beta(1-\alpha)\ln L_2 + (1+\beta^2)(1-\alpha)L_0 + \lambda\left [A_1 + \frac{w_2(L_0-L_2)}{(1+r)}-\sum_{t=1}^3\frac{C_t}{(1+r)^{t-1}} \right]
$$

Repeating the process above yields

$$
\begin{aligned}
h_2^F(w_2, \lambda)&=L_0-\frac{\beta(1-\alpha)(1+r)}{\lambda w_2} \\
h_2^M(w_2, \lambda^*, t)&=L_0-\frac{\gamma''(1-\alpha)}{w_2}
\end{aligned}
$$
where

$$
\gamma''=\frac{(1-\beta[(1+r)A_1+w_2L_0])}{(1+r)[\alpha(1-\beta^3)+(1-\alpha)\beta(1-\beta)]}
$$